Notes on generating initial models for mapping into {\tt MAESTRO}

### 2008-10-11 docs/initial_models/paper.tex
update the locations of the various initial models and the generation routines.

{\tt test2} & \rightarrow & {\tt ???} \nonumber \\
{\tt test\_convect} & \rightarrow & {\tt ???} \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt ???} \nonumber \\
{\tt spherical\_heat} & \rightarrow & {\tt ???} \nonumber \\

@@

{\tt test2} & \rightarrow & {\tt ???} \nonumber \\
{\tt test\_convect} & \rightarrow & {\tt ???} \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt ???} \nonumber \\
{\tt spherical\_heat} & \rightarrow & {\tt ???} \nonumber \\

>>>>

{\tt test2} & \rightarrow & \mathrm{comes~from~the~ {\tt lmn\_bubble\_burn}~setup~in~ {\tt FLASH}} \nonumber \\
{\tt test\_convect} & \rightarrow & \mathrm{comes~from~the~ {\tt lmn\_convect}~setup~in~ {\tt FLASH}} \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt initial\_models/kepler/model\_6.e8.raw} \nonumber \\
{\tt spherical\_heat} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \\

@@

{\tt test2} & \rightarrow & \mathrm{comes~from~the~ {\tt lmn\_bubble\_burn}~setup~in~ {\tt FLASH}} \nonumber \\
{\tt test\_convect} & \rightarrow & \mathrm{comes~from~the~ {\tt lmn\_convect}~setup~in~ {\tt FLASH}} \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt initial\_models/kepler/init\_1d.f90} \nonumber \\
{\tt spherical\_heat} & \rightarrow & {\tt initial\_models/spherical/init\_1d.f90} \nonumber \\
